---
title: "Plotly"
output: 
  html_document:
    toc: true
    toc_float: true
---

# Loading Packages

```{r, message = FALSE, warning = FALSE}
library(tidyverse)

library(p8105.datasets)

library(plotly)
```

# Loading Data

```{r}
data("ny_noaa")

ny_noaa =
  ny_noaa %>%
separate(col = date,   into = c("year", "month", "day"), sep = "-", convert = TRUE) %>%
mutate(
   year = as.character(year),
   month = as.character(month),
   tmax = as.numeric(tmax),
   tmin = as.numeric(tmin),
   tmax = tmax / 10,
   tmin = tmin / 10,
   prcp = prcp / 10) %>%
  filter(
    year == 2000,
    day %in% 24:31) %>%
  drop_na(tmax) %>%
  drop_na(tmin) %>%
  drop_na(prcp) %>%
  drop_na(snow) %>%
  drop_na(snwd)
 
head(ny_noaa)  

```

# Plots Made by Plotly

## Barplot
```{r}
ny_noaa %>%
  count(id) %>%
  mutate(id = fct_reorder(id, n)) %>%
  plot_ly(x = ~id,y = ~n, color = ~id, type = "bar", colors = "viridis") %>%
  layout(
    title = "Counts of Weather Station IDs",
    xaxis = list(title = "Weather Station ID"),
    yaxis = list(title = "Count")
  )
```

This is a barplot of the counts of weather station IDs during the last 7 or 8 days of every month in the year 2000.

## Boxplot

```{r}
ny_noaa %>%
  mutate(Month = fct_reorder(month, tmin)) %>%
  plot_ly(
    y = ~tmin, color = ~month,
    type = "box", colors = "viridis") %>%
  layout(
    title = "The Minimum Temperature for Each Month in 2000",
    xaxis = list(title = "Month Number"),
    yaxis = list(title = "Minimum Temperature (C)")
  )
```

This is a boxplot of the minimum temperature during the last 7 or 8 days of the every month in the year 2000.

## Scatterplot

```{r}
ny_noaa %>%
  plot_ly(
    x = ~prcp, y = ~snow, color = ~day,text = ~id,
    alpha = .5, type = "scatter", mode  = "markers") %>%
  layout(
    title = "Precipitation by Snowfall",
    xaxis = list(title = "Precipitation (mm)"),
    yaxis = list(title = "Snowfall (mm)")
  )
```

This is a scatterplot of precipitation by snowfall during the last 7 or 8 days of every month during the year 2000.



